Modern Graph Generators: A Survey

### 2018-09-01 challenges.tex
Temporal gaphs - update

\subsection{Evolving Graph Data}
As user requirements as well as environments change, most of the existing
applications naturally evolve over time, at least to some extent. This evolution
usually influences the structure of the data and consequently all the related
parts of the application (i.e., storage strategies, operations, indexes etc.).
The respective data generator should hence be able to simulate such a growth
and/or change in structure.

In some graph applications, such as, e.g., social networks, the evolution of the
data is a significant aspect, especially in the activity graphs, that has been
studied
extensively~\cite{doreian1997evolution,Kumar:2006:SEO:1150402.1150476,Hellmann2014583,wang2013,Kossinets88,Viswanath:2009:EUI:1592665.1592675}.
A related problem is \emph{data versioning} and respective ability to query
across multiple versions of data or to carry out general analysis. 
%Considering graph
%data this problem is also common, for example  in the area of Linked
This problem has been investigated for instance within the domain of Linked
Open Data~\cite{DBLP:conf/semweb/Papakonstantinou16,DBLP:conf/esws/MeimarisP16,fernandez2015towards,fernandez2015bear}.

As shown in~\cite{Leskovec:2005:RMT:2101235.2101254,Leskovec:2005:GOT:1081870.1081893},
evolving graphs have further specific features. For example, some graphs grow
over time according to a \emph{densification power law} which means that real
graphs tend to sprout many more edges than nodes, and thus are densifying as
they grow. Also the effective diameter of graphs tends to shrink or stabilize as
the graph grows with time.

>>>>

\subsection{Evolving Graph Data}
As user requirements as well as environments change, most of the existing
applications naturally evolve over time, at least to some extent. This evolution
usually influences the structure of the data and consequently all the related
parts of the application (i.e., storage strategies, operations, indexes etc.).
In the world of graph data such graphs that change with time are denoted as \emph{evolving}, \emph{temporal}, \emph{dynamic}, or \emph{time-varying}. They can be viewed as labeled graphs, where the labels capture some measure of time~\cite{Michail2015}.

The evolution of graphs can be considered variously. We can assume a static set of nodes and a varying set of edges.  Or, there are applications where the graphs only ``grow'', i.e., the set of nodes and/or edges is only extended with new items. In the most general case we can assume any changes in both set of nodes and set of edges. Anyway with the evolution aspect the complexity of classical graph problems increases significantly~\cite{Michail2015,Wu:2014:PPT:2732939.2732945}. In some graph applications, such as, e.g., social networks, the evolution of the
data is a significant aspect, especially in the activity graphs~\cite{doreian1997evolution,Kumar:2006:SEO:1150402.1150476,Hellmann2014583,wang2013,Kossinets88,Viswanath:2009:EUI:1592665.1592675}.
However, as shown in~\cite{Leskovec:2005:RMT:2101235.2101254,Leskovec:2005:GOT:1081870.1081893},
evolving graphs have further specific features. For example, some graphs grow over time according to a \emph{densification power law} which means that real graphs tend to sprout many more edges than nodes, and thus are densifying as they grow. Also the effective diameter of graphs tends to shrink or stabilize as the graph grows with time.

A related problem is \emph{data versioning} and respective ability to query across multiple versions of data or to carry out general analysis. 
%Considering graph
%data this problem is also common, for example  in the area of Linked
This problem has been investigated for instance within the domain of Linked
Open Data~\cite{DBLP:conf/semweb/Papakonstantinou16,DBLP:conf/esws/MeimarisP16,fernandez2015towards,fernandez2015bear}.

The respective data generator should hence be able to simulate a natural growth and/or changes in the structure of the graph with regards to the various features of distinct use cases. However,  even though the area of dynamic graphs is intensively studied, surprisingly there seem to exist only very few proposals of a respective generator.

In~\cite{GoerkeKlugeSchumm2012_1000029825} the authors focus on \emph{clustering dynamic graphs}, i.e. graphs where the clustering corresponds to the partition of nodes into natural groups based on the paradigm of intra-cluster density versus inter-cluster sparsity of edges. The generator generates a time series of random graphs $G_0, G_1, ... G_n$, where $G_t$ emerges from $G_{t-1}$ via atomic updates, i.e., the insertion or deletion of an edge or vertex. The generator keeps track of a (dynamic) ground truth clustering. The probability of atomic events is chosen in a way that adheres to this clustering, without losing randomness.

A recent proposal of a generator~\cite{mlg2018_42} of temporal graphs results from the observation that small subgraph patterns in networks, called \emph{network motifs} or \emph{graphlets}, are crucial indicators of the structure and the evolution of the graphs~\cite{Paranjape:2017:MTN:3018661.3018731}. For a given graph $G$ and a predefined ordered list of structural atomic motifs $M$ the generator first computes the distribution of the motifs in the graph. The distribution is then used to generate a synthetic graph with the same features.
